TacticToe: Learning the Game of Tactics

### 2018-02-02 tactictoe_jv.tex
interactive example

\subsection{The problem}
How a user works with an ITP and how this gives rise to a machine learning 
problem.
Two ways of representing a formulas.
Definition of a tactic in \holfour. In this research, we will take the definition
that a tactic takes a goal and returns a list of goals.
Input of the prediction: goal
If a tactic produces no goals then its input goal is solved.

@@

In order to apply machine learning to the existing proof scripts, we will need 
to
parse and modify them, which involves parsing and modification of \sml code.
Acquiring access to the string representation of a tactic (code for the tactic) 
allows us generating
proof scripts that can be inspected by a human.
As some \holfour theories are built in separate sessions, it is not possible
to transfer \sml values directly, but instead tactic code needs to transferred 
instead.
To do this, the transferred information will be saved externally.

@@

@@

\todoi{Is copied and modified}
We proposed a new proof assistant automation technique which combines 
tactic-based proof search with machine learning tactic prediction
Its implementation,
\tactictoe, achieves an overall performance of 59\% theorems on 7088 theorems  
of the \holfour standard library surpassing \eprover with 
auto-schedule. Its 
effectiveness is especially visible on 
theories which use inductive data structures, specialized decision procedures, 
and custom built simplification sets.
Thanks to the learning abilities of \tactictoe, the generated proof scripts 
usually reveal the high-level structure of the proof. %For these reasons, 
We therefore believe that predicting ITP tactics based on the current goal 
features is a very reasonable approach to automatically guiding proof search, 
and that accurate predictions can be obtained by learning from the knowledge 
available in today's large formal proof corpora. 
%And it seems to get us 
%closer to the way how humans learn to do theorem proving.

>>>>

\subsection{The problem}
How a user works with an ITP and how this gives rise to a machine learning 
problem.
Two ways of representing a formulas.
Definition of a tactic in \holfour. In this research, we will take the definition
that a tactic takes a goal and returns a list of goals.
Input of the prediction: goal
If a tactic produces no goals then its input goal is solved.
Define tactical etc maybe import graphic that explain how tactic works form the 
presentations.

@@

@@

Interactive usage example.

\begin{lstlisting}[language=SMLSmall]
tactictoe ([], ``countable (UNIV:num set)``);
let fun RWTAC thms = SRW_TAC [] thms in RWTAC [(fetch "pred_set" 
"countable_def"), (fetch "pred_set" "INJ_DEF")] THEN Q.EXISTS_TAC `\\x.x` THEN 
METIS_TAC [] end
\end{lstlisting}

\begin{lstlisting}[language=SMLSmall]
tactictoe ([], ``count (n+m) DIFF count n = IMAGE ($+n) (count m)``);
SRW_TAC [ARITH_ss] [(fetch "pred_set" "EXTENSION"), EQ_IMP_THM] THEN 
Q.EXISTS_TAC `x - n` THEN SRW_TAC [ARITH_ss] []
\end{lstlisting}

@@

\todoi{Is copied and modified}
We proposed a new proof assistant automation technique which combines 
tactic-based proof search with machine learning tactic prediction
Its implementation,
\tactictoe, achieves an overall performance of 66.2\% theorems on 7164 
theorems  
of the \holfour standard library surpassing \eprover with 
auto-schedule. Its 
effectiveness is especially visible on 
theories which use inductive data structures, specialized decision procedures, 
and custom built simplification sets.
Thanks to the learning abilities of \tactictoe, the generated proof scripts 
usually reveal the high-level structure of the proof. %For these reasons, 
We therefore believe that predicting ITP tactics based on the current goal 
features is a very reasonable approach to automatically guiding proof search, 
and that accurate predictions can be obtained by learning from the knowledge 
available in today's large formal proof corpora. 
%And it seems to get us 
%closer to the way how humans learn to do theorem proving.
